The Effects of Stellar Binarity on Transit Survey Occurrence Rates

### 2017-10-05 paper/ms.tex
update MC numbers given bugfix

For planets detected in binary systems,
\begin{equation}
N_{{\rm det},d}
= 
N_d \Gamma_{t,d} (f_{d1,g}f_{d1,c} + f_{\rm desired}w_{d2}f_{d2,g}f_{d2,c}).
\label{eq:N_det_d_model2}
\end{equation}
The factor $f_{\rm desired}$, as previously discussed, accounts for the 
fraction of secondaries not of the desired {\it stellar} type. The above 
counts the total number of detected planets around stars of the desired type, 
though all these planets have diluted radii.
The detection and geometric transit probabilities for a given system are
\begin{align}
f_{d1,c} &= (1+\gamma_R)^{-3} \\
f_{d1,g} &= f_{s,g} \\
f_{d2,c} &= (1+\gamma_R^{-1})^{-3} \gamma_R^{-6/\alpha} 
\label{eq:f_d2c}\\
f_{d2,g} &= f_{s,g}q^{2/3},
\end{align}
where typically $\alpha=3.5$ (and the second term in Eq.~\ref{eq:f_d2c} comes 
from the stellar radius correction).
For a typical binary drawn from the local stellar neighborhood, $\gamma_R 
\approx 0.2$ (see Fig.~\ref{fig:gammaR_distribn_mag_limited}), and there is an 
interesting asymmetry.
One finds the completeness for planets which orbit the primary star, 
$f_{d1,c}$ to be
\begin{equation}
f_{d1,c} = (1+\gamma_R)^{-3} \sim 70\%
\end{equation}
However, for planets which orbit the secondary star, the completeness is
\begin{equation}
f_{d2,c} = (1+\gamma_R^{-1})^{-3} \gamma_R^{-6/\alpha} \sim 7\%.
\end{equation}
Controlling for all other variables, in the typical binary system planets 
around secondaries are more difficult to detect than those around primaries.

@@

Instead, we run a Monte Carlo simulation in which we fix the planet and 
primary star properties, draw the binary mass ratio from 
Eq.~\ref{eq:pdf_q_mag_limited}, 
and take the luminosity as $L\propto M^{3.5}$. We find 
a mean of 
\begin{equation}
\langle X_\Gamma \rangle =1.289\quad ({\rm lower\ limit\ from\ Monte\ Carlo}),
\label{eq:X_Gamma_model2_lower}
\end{equation}
and a median that is the same to within one percent.
This value is comparable to what one would guess using the analytic results 
for $\langle N_d \rangle / N_s$ to substitute $\beta$, and $\gamma_R$ to 
compute $f_{d1,c}$.

>>>>

For planets detected in binary systems,
\begin{equation}
N_{{\rm det},d}
= 
N_d \Gamma_{t,d} (f_{d1,g}f_{d1,c} + f_{\rm desired}w_{d2}f_{d2,g}f_{d2,c}).
\label{eq:N_det_d_model2}
\end{equation}
The factor $f_{\rm desired}$, as previously discussed, accounts for the 
fraction of secondaries not of the desired {\it stellar} type. The above 
counts the total number of detected planets around stars of the desired type, 
though all these planets have diluted radii.
The detection and geometric transit probabilities for a given system are
\begin{align}
f_{d1,c} &= (1+\gamma_R)^{-3} \\
f_{d1,g} &= f_{s,g} \\
f_{d2,c} &= (1+\gamma_R^{-1})^{-3} \gamma_R^{-6/\alpha} 
\label{eq:f_d2c}\\
f_{d2,g} &= f_{s,g}q^{2/3},
\end{align}
where typically $\alpha=3.5$ (and the second term in Eq.~\ref{eq:f_d2c} comes 
from the stellar radius correction).
For a typical binary drawn from the local stellar neighborhood, $\gamma_R 
\approx 0.2$ (see Fig.~\ref{fig:gammaR_distribn_mag_limited}), and there is an 
interesting asymmetry.
One finds the completeness for planets which orbit the primary star, 
$f_{d1,c}$ to be
\begin{equation}
f_{d1,c} \sim 70\% \quad(\alpha=3.5, \gamma_R=0.2).
\end{equation}
However, for planets which orbit the secondary star, the completeness is
\begin{equation}
f_{d2,c} \sim 7\% \quad(\alpha=3.5, \gamma_R=0.2).
\end{equation}
This is the obvious statement that controlling for all other variables, 
in the typical binary system planets around secondaries are more difficult to 
detect than those around primaries.

@@

Instead, we run a Monte Carlo simulation in which we fix the planet and 
primary star properties, draw the binary mass ratio from 
Eq.~\ref{eq:pdf_q_mag_limited}, 
and take the luminosity as $L\propto M^{3.5}$. We find a mean occurrence 
correction of 
\begin{equation}
\langle X_\Gamma \rangle =1.268\quad ({\rm lower\ limit\ from\ Monte\ Carlo}),
\label{eq:X_Gamma_model2_lower}
\end{equation}
and a median that is the same to within one percent.
This value is comparable to what one would guess using the analytic results 
for $\langle N_d \rangle / N_s$ to substitute $\beta$, and $\gamma_R$ to 
compute $f_{d1,c}$.
